---
title: "Supplementary figures"
# author: "Tom Ellis"
date: ""
output:
  bookdown::pdf_book:
    toc: no
    keep_tex: no
    number_sections: false
    latex_engine: lualatex
  bookdown::word_document2: null
---
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

This document contains supplementary figures to accompany the manuscript "A major virus-resistance QTL in *Arabidopsis thaliana* is consistent with negative frequency-dependent selection".

```{r supp-setup}
knitr::opts_chunk$set(
  echo = FALSE, cache=T, cache.lazy=T,
  fig.width=16.9/2.54, fig.height = 10/2.54, fig.align='center',
  warning = F, message =F,
  dev = "png"
)

library(tidyverse)
source("02_library/manhattan_plot.R")
```

(ref:conditional-gwas) Manhattan plots for the association between SNPs and necrosis including the SNP at Chr:5,923,326 as a cofactor. Results are shown for (A) common effects in response to both viral isolates and (B) virus-specific responses.

```{r conditional-gwas, fig.cap="(ref:conditional-gwas)"}

path <- "05_supplementary_figures/GWA_condition_on_top_SNP/output/"
conditional_gwas <- list(
  g = read_csv(
    paste(path, "Necrosis_Evo_Necrosis_Anc_0.1_MTMM_G.csv", sep = ""),
    col_types = 'ciddid'
  ),
  gxe = read_csv(
    paste(path, "Necrosis_Evo_Necrosis_Anc_0.1_MTMM_GxE.csv", sep = ""),
    col_types = 'ciddid'
  )
)


ggpubr::ggarrange(
  manhattan_plot(conditional_gwas$g) +
    ggtitle("Common effects") +
    lims(y = c(0, 6e-5)),
  manhattan_plot(conditional_gwas$gxe) + 
    ggtitle("Virus-specific effects") +
    lims(y = c(0, 3e-8)),
  ncol= 2, labels = "AUTO"
)

```

(ref:g-manh) Manhattan plots for associations with common disease responses to both viral isolates.

```{r g-manh, fig.cap="(ref:g-manh)", fig.height=20/2.54}
# Import files for G results
limix_path <- "04_main_figures/02_multitrait_GWA/output/"
limix_files <- list.files(limix_path, "*_G.csv")
limix_files <-paste(limix_path, limix_files, sep ="")

limix_G <- lapply(limix_files, read_csv, col_types = 'ciddid')
names(limix_G) <- c("audps", "inf", "necrosis", "sym")

ggpubr::ggarrange(
  manhattan_plot(limix_G$audps) + ggtitle("AUDPS"),
  manhattan_plot(limix_G$inf)   + ggtitle("Infectivity"),
  manhattan_plot(limix_G$sym)   + ggtitle("Severity of symptoms"),
  manhattan_plot(limix_G$necrosis) + ggtitle("Necrosis"),
  nrow=2, ncol= 2, labels = "AUTO"
)

```

(ref:gxe-manh) Manhattan plots for associations with disease responses specific to individual viral isolates.

```{r gxe-manh, fig.cap="(ref:gxe-manh)", fig.height=20/2.54}

# Import files for GxE results
limix_path <- "04_main_figures/02_multitrait_GWA/output/"
limix_files <- list.files(limix_path, "*_GxE.csv")
limix_files <-paste(limix_path, limix_files, sep ="")

limix_GxE <- lapply(limix_files, read_csv, col_types = 'ciddid')
names(limix_GxE) <- c("audps", "inf", "necrosis", "sym")


ggpubr::ggarrange(
  manhattan_plot(limix_GxE$audps) + ggtitle("AUDPS"),
  manhattan_plot(limix_GxE$inf) + ggtitle("Infectivity"),
  manhattan_plot(limix_GxE$sym) + ggtitle("Severity of symptoms"),
  manhattan_plot(limix_GxE$necrosis) + ggtitle("Necrosis"),
  nrow=2, ncol= 2, labels = "AUTO"
)

```


(ref:replicate-expt) Manhattan plots for the association between SNPs and necrosis in the replicate dataset of 118 accessions.

```{r replicate-expt, fig.cap="(ref:replicate-expt)", fig.width=16.9/2.54, fig.height=10/2.54}
path <- "05_supplementary_figures/replicate_dataset/output/all_snps/"
read_csv(
    paste(path, "binary_necrosis_anc_binary_necrosis_evo_0.1_MTMM_G.csv", sep = ""),
    col_types = 'ciddid'
  ) %>% 
  manhattan_plot()

```

(ref:kruskal-wallis) Manhattan plots for the association between SNPs and necrosis using a Kruskall-Wallis test at each locus, with no correction for population structure.

```{r kruskal-wallis, fig.cap="(ref:kruskal-wallis)", eval=F}

path <- "005_results/017_kruskall-wallis_gwas/output/"

# kw_anc <- read_csv_chunked(
#   paste(path, "ancestral.csv", sep = ""),
#   callback = DataFrameCallback$new(function(x, pos) subset(x, maf > 0.1)),
#   col_types = 'ciddid',
#   progress = F) %>% 
#   manhattan_plot() +
#     ggtitle("TuMV-Anc")


kw_evo <- read_csv_chunked(
  paste(path, "evolved.csv", sep = ""),
  callback = DataFrameCallback$new(function(x, pos) subset(x, maf > 0.1)),
  col_types = 'ciddid',
  progress = F) %>%
  manhattan_plot() +
    ggtitle("TuMV-Evo")


# ggpubr::ggarrange(
#   kw_anc, kw_evo,
#   ncol= 2, labels = "AUTO"
# )




```

